An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-13 EconGrowth.Rnw
Using the new standardScatterPlot code for the first single-factor resampling graph.

<<Unconverged_Frac_Table, results='asis', eval=TRUE>>=
printFracUnconvergedXtable()
@

@@

<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
sfResamplePlot(factor="K")
@

@@

Converting the resampling data to 95\% confidence intervals
provides results shown in 
Figures~\ref{fig:SFk_Params_Graph}--\ref{fig:SFu_Params_Graph}.

>>>>

<<Unconverged_Frac_Table, results='asis'>>=
printFracUnconvergedXtable()
@

@@

<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="K", 
                                        countryAbbrevsOrder=countryAbbrevsForGraph,
                                        countryAbbrevsOrderU=countryAbbrevsForGraphU), 
                    aes(m, lambda)) + 
  labs(x=expression(alpha), y=expression(lambda))
@

@@

Converting the resample model coefficient data to 95\% confidence intervals
gives the results shown in 
Figures~\ref{fig:SFk_Params_Graph}--\ref{fig:SFu_Params_Graph}.
